Parsing Tweets into Universal Dependencies

### 2017-12-14 paper.tex
add more word on the compared system, fit into 8 pages.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 11cm 9cm},clip]{graphics/bilstm_tokenizer}
	\caption{The bi-LSTM tokenizer that segments `{\it its gonna be}' into `{\it it s gon na be}'.}\label{fig:tok-model}
\end{figure}
We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
Figure \ref{fig:tok-model} shows our tokenization model.
Space is treated as an input but deterministically \nascomment{check
  here}  assigned a special tag \$.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}. We therefore consider existing POS taggers for tweets instead of developing our own.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger
(both greedy and CRF variants), and 
\citet{ma-hovy:2016:P16-1}'s neural network POS tagger 
which has the state-of-the-art performance  on Penn Treebank data.
 %and also two bi-LSTM systems similar
%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use Twitter-specific Glove embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rccc}
		\hline
		\it System & UAS & LAS & Kt/s \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 & 0.3 \\
		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 & 1.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 & 2.3 \\
		\hdashline
		Ensemble (20) & 83.5 & 79.4 & 0.2 \\
		Distillation ($\alpha =1.0$) & 82.2 & 78.0 & 2.3 \\
		Distillation ($\alpha =0.9$) & 82.4 & 78.1 & 2.3 \\		
		Distillation w/ exploration & 82.5 & 78.4 & 2.3 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. The ``Kt/s'' column shows
           the parsing speed evaluated by thousands of tokens
           the model processed per second. For fair comparison, we limit the
           number of CPUs used in \citet{DBLP:journals/corr/DozatM16} experiments to 1.
            \label{tbl:parse-result}}
\end{table}

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
 parsers requiring superlinear runtime. 
Both of the comparison systems are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth,trim={0 0 11cm 9cm},clip]{graphics/bilstm_tokenizer}
	\caption{The bi-LSTM tokenizer that segments `{\it its gonna be}' into `{\it it s gon na be}'.}\label{fig:tok-model}
\end{figure}
We introduce a new
character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
for tokenization.
Our model takes the raw sentence and tags each character in this 
sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
Figure \ref{fig:tok-model} shows our tokenization model.
Space is treated as an input but deterministically  assigned a special tag \$.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}. We therefore consider existing POS taggers for tweets instead of developing our own.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger
(both greedy and CRF variants), and 
\citet{ma-hovy:2016:P16-1}'s neural network tagger 
which achieves the state-of-the-art performance on PTB.
\citet{gui-EtAl:2017:EMNLP20172} presented the state-of-the-art neural tagger for Twitter,
but their code didn't work beyond PTB tag set. Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
 %and also two bi-LSTM systems similar
%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All compared systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use Twitter-specific Glove embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rccc}
		\hline
		\it System & UAS & LAS & Kt/s \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 & 0.3 \\
		\citet{dozat-qi-manning:2017:K17-3} & 81.9 &  77.7 & 1.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 & 2.3 \\
		\hdashline
		Ensemble (20) & 83.5 & 79.4 & 0.2 \\
		Distillation ($\alpha =1.0$) & 82.2 & 78.0 & 2.3 \\
		Distillation ($\alpha =0.9$) & 82.4 & 78.1 & 2.3 \\		
		Distillation w/ exploration & 82.5 & 78.4 & 2.3 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2},
           with automatic POS tags. The ``Kt/s'' column shows
           the parsing speed evaluated by thousands of tokens
           the model processed per second. For fair comparison, we limit the
           number of CPUs used in \citet{dozat-qi-manning:2017:K17-3} experiments to 1.
            \label{tbl:parse-result}}
\end{table}

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \citet{kong-EtAl:2014:EMNLP2014}'s parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses the biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system. \yjcomment{i briefly describ the compared systems.}
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.
